\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2019-01-15 bare_conf.tex
some corrections according to review.

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\documentclass[10pt]{IEEEtran}
\usepackage{times}
\usepackage{color}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{hyperref}

@@

\pagestyle{empty}
\begin{document}
\pagenumbering{gobble}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}} % \\[-1.5ex] and subtitle}\\[0.2ex]}

@@

@@

\begin{IEEEkeywords}
computer vision; deep learning; mobile application; aid for blind and visually impaired; audio feedback; tactile feedback; impaired human vision compensation; user-centered design.%
\end{IEEEkeywords}
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:introduction}
More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better. However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Dunai}. Such systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane. This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and are used to (smartphone). This paper describes a high level architecture of the technology aid for visually impaired people utilizing the latest achievements in the field of computer vision.

@@

User-centered design sessions with visually impaired persons and analysis of the aforementioned data sources provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}). The process made it clear that understanding of the user needs was limited in the project team. Based on the results of the user-centered design process, scientific publications and patent analysis, we present the outline of the system for impaired human vision compensation.

@@

\begin{thebibliography}{1}

@@

\bibitem{Carroll} Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.

>>>>

% Note that the a4paper option is mainly intended so that authors in
% countries using A4 can easily print to A4 and see how their papers will
% look in print - the typesetting of the document will not typically be
% affected with changes in paper size (but the bottom and side margins will).
% Use the testflow package mentioned above to verify correct handling of
% both paper sizes by the user's LaTeX system.
%
% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
% should be used if it is desired that the figures are to be displayed in
% draft mode.
%
\documentclass[10pt,conference,compsocconf]{IEEEtran}
%\documentclass[10pt]{IEEEtran}
\usepackage{times}
\usepackage{color}
\usepackage{caption}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{etoolbox}

@@

\pagestyle{empty}

\begin{document}
\pagenumbering{gobble}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
\title{\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}} % \\[-1.5ex] and subtitle}\\[0.2ex]}

@@

\setlength{\parskip}{0.1em} % reduce spacings between paragraphs

@@

\begin{IEEEkeywords}
computer vision; deep learning; mobile application; aid for blind and visually impaired; audio feedback; tactile feedback; impaired human vision compensation; user-centered design.%
\end{IEEEkeywords}
% For peer review papers, you can put extra information on the cover
% page as needed:
% \ifCLASSOPTIONpeerreview
% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
% \fi
%
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
\IEEEpeerreviewmaketitle
\section{Introduction}
\label{sec:introduction}
More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world better. However, computer vision is a rapidly evolving field; systems based on the aforementioned approaches become outdated in a relatively short time and often lack accuracy and reliability in real-world conditions in comparison to the state-of-the-art technologies. In this article, we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Dunai}. Such systems often lack convenience and bring additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane. This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired persons already have on-hand and are used to (smartphone). This paper describes a high level architecture of the technology aid for visually impaired people utilizing the latest achievements in the field of computer vision.

% corr start
This paper is structured as follows. We start our presentation with Section~\ref{sec:method}, which describes the methodological foundations of this research. Section~\ref{sec:results} detalizes the architecture of the aforementioned system. Finally, Section~\ref{sec:discussion} summarizes and discusses the results of conducted analysis.
% corr end

@@

User-centered design sessions with visually impaired persons and analysis of the aforementioned data sources provided substantial input for the design of the proposed system (Figure~\ref{fig:schematics}). The process made it clear that understanding of the user needs was limited in the project team. Based on the results of the user-centered design process, scientific publications and patent analysis, we present the outline of the system for impaired human vision compensation.

@@

\begin{thebibliography}{99}

@@

\bibitem{Carroll} \noindent Carroll, J. M., Rosson, M. B. Participatory design in community informatics. Des. Stud., vol. 28, no. 3, pp. 243-261, May 2007.
